---
title: "DATA605_HW4"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(root.dir=normalizePath("C:\\Users\\irene\\OneDrive\\Documents\\R\\DATA605\\jpg"))
memory.size(max = T)
library(EBImage)
library(doParallel)
library(jpeg)
library(kableExtra)
library(OpenImageR)
```

## Preparation

There are 17 files here so preparing the data.

```{r}
files=list.files("C:\\Users\\irene\\OneDrive\\Documents\\R\\DATA605\\jpg",pattern="\\.jpg")[1:17]
```

## Function to view the shoes

```{r}
height=1200; width=2500;scale=20 
plot_jpeg = function(path, add=FALSE)
{ jpg = readJPEG(path, native=T) # read the file
  res = dim(jpg)[2:1] # get the resolution, [x, y]
  if (!add) # initialize an empty plot area if add==FALSE
    plot(1,1,xlim=c(1,res[1]),ylim=c(1,res[2]),asp=1,type='n',xaxs='i',yaxs='i',xaxt='n',yaxt='n',xlab='',ylab='',bty='n')
  rasterImage(jpg,1,1,res[1],res[2])
}
```

## Data loaded to array

The data is loaded into an array 'im'. This array contains length, height and channels of the files.

```{r}
im=array(rep(0,length(files)*height/scale*width/scale*3), dim=c(length(files), height/scale, width/scale,3))

for (i in 1:17){
  temp=resize(readJPEG(paste0("C:\\Users\\irene\\OneDrive\\Documents\\R\\DATA605\\jpg\\", files[i])),height/scale, width/scale)
  im[i,,,]=array(temp,dim=c(1, height/scale, width/scale,3))}
```

## Vectorize

A for loop goes from 1 to 17 filling up the 3 channel vectors into a matrix 'flat'. This matrix is converted into a dataframe.

```{r}
flat=matrix(0, 17, prod(dim(im))) 
for (i in 1:17) {
  newim <- readJPEG(paste0("C:\\Users\\irene\\OneDrive\\Documents\\R\\DATA605\\jpg\\", files[i]))
  r=as.vector(im[i,,,1]); g=as.vector(im[i,,,2]);b=as.vector(im[i,,,3])
  flat[i,] <- t(c(r, g, b))
}
shoes=as.data.frame(t(flat))
```

## Plots

Creating plots for the images(just the first ones).

```{r}
par(mfrow=c(3,3))
par(mai=c(.3,.3,.3,.3))
for (i in 1:17){  
plot_jpeg(writeJPEG(im[i,,,]))
}
```

## Eigencomponents from Correlation Structure

The shoes dataframe is scaled. z transformation is taking place here.
scaled has mean as 0 and standard deviation 1

```{r}
scaled=scale(shoes, center = TRUE, scale = TRUE)
mean.shoe=attr(scaled, "scaled:center") 
std.shoe=attr(scaled, "scaled:scale")  

Sigma_=cor(scaled) # Corelation (Covariance)
```

### Eigencomponents

Cumulative proportion of variability is derived here,ie., variability associated with each value is converted to the cumulative proportion of it.

```{r}
myeigen=eigen(Sigma_)
cumsum(myeigen$values) / sum(myeigen$values)
```

## Eigenshoes

The task here is to visualize eigenimagery that accounts for 80% of the variability so we take the first 2 only.

```{r}
scaling=diag(myeigen$values[1:2]^(-1/2)) / (sqrt(nrow(scaled)-1))
eigenshoes=scaled%*%myeigen$vectors[,1:2]%*%scaling
imageShow(array(eigenshoes[,1], c(60,125,3)))
```

