---
title: "DATA605_HW11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PROBLEM STATEMENT

Using the “cars” dataset in R, build a linear model for stopping distance as a function of speed and replicate the analysis of your textbook chapter 3 (visualization, quality evaluation of the model, and residual analysis.)

## Head

View the first 5 records in the "cars" dataset.

```{r}
head(cars)
```

## Summary

To get an idea on the data viewing the summary below.

```{r}
summary(cars)
```

## Data Visualization

Here *speed* is the independent variable and *dist* is the dependent variable. Plotting the dataset below to see how the distance increases as the speed increases. (I have used different colors to identify it better).

```{r}
plot(cars,col=c("brown","blue"))
```

### Histogram

```{r}
hist(cars$speed)
hist(cars$dist)
```

## Linear Model

```{r}
L <- lm(dist ~ speed, cars)
summary(L)
```

*intercept* is -17.5791 and *slope* is 3.9324. 

So the One-Factor Regression Model is:

$dist = -17.5791 + 3.9324 * speed$

## Plot with linear model

```{r}
plot(cars,col=c("brown","orange"))
abline(L,col="blue")
```

## Residual Plot

```{r}
plot(fitted(L), resid(L))
```

## Q-Q Plot

It can be seen below that there is some right skew.

```{r}
qqnorm(resid(L),col="blue")
qqline(resid(L),col="green")
```