---
title: "DATA605 HW7"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.

Let X1, X2, . . . , Xn be n mutually independent random variables, each ofwhich is uniformly distributed on the integers from 1 to k. Let Y denote the minimum of the Xi’s. Find the distribution of Y .

$P(X=1)=\frac{(k-y+1)^{n}-(k-y)^{n}}{k^{n}}$

# 2.

Your organization owns a copier (future lawyers, etc.) or MRI (future doctors).  This machine has a manufacturer’s expected lifetime of 10 years.  This means that we expect one failure every ten years.

## a.

What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a geometric.  (Hint: the probability is equivalent to not failing during the first 8 years..)

```{r}
pgeom(8, 0.1, lower.tail = F)
```

$E(X)=\frac{1}{λ}=\frac{1}{0.1}=10$
$\sigma=\sqrt\frac{1}{λ^2}=\frac{1}{λ}=\frac{1}{0.1}=10$

## b.

What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as an exponential.

```{r}
pexp(8, 0.1, lower.tail = F)
```

$E(X)=np=8*0.1=0.8$
$\sigma=\sqrt(npq)=\sqrt(8*0.1*0.9)=0.8485$

## c.

What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a binomial.  (Hint:  0 success in 8 years)   

```{r}
pbinom(0, 8, 0.1)
```

$E(X)=np=8*0.1=0.8$
$\sigma=\sqrt(npq)=\sqrt(8*0.1*0.9)=0.8485$

## d.

What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a Poisson

```{r}
dpois(8, 10)
```

$E(X)=μ=10$
$\sigma=\sqrtμ=3.1623$