---
title: "DATA605_HW12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PROBLEM STATEMENT

The who.csv data set contains realworld data from 2008. The variables included follow:

Country: name of the country

LifeExp: average life expectancy for the country in years

InfantSurvival: proportion of those surviving to one year or more

Under5Survival: proportion of those surviving to five years or more

TBFree: proportion of the population without TB.

PropMD: proportion of the population who are MDs

PropRN: proportion of the population who are RNs

PersExp: mean personal expenditures on healthcare in US dollars at average exchange rate

GovtExp: mean government expenditures per capita on healthcare, US dollars at avg exchange rate

TotExp: sum of personal and government expenditures.

### Load Dataset

```{r}
WHO <- read.csv('https://raw.githubusercontent.com/irene908/DATA605/main/who.csv')
head(WHO)
```

## 1. 

Provide a scatterplot of LifeExp~TotExp, and run simple linear regression.  Do not transform the variables. Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss whether the assumptions of simple linear regression met.

```{r}
WHO.L<-lm(LifeExp ~ TotExp,WHO)

# Scatter Plot
plot(LifeExp ~ TotExp, WHO)
abline(WHO.L,col="red")

#Linear regression summary
summary(WHO.L)

# residual plot
plot(fitted(WHO.L), resid(WHO.L))
abline(h=0)

# Q-Q Plot of residual
qqnorm(resid(WHO.L))
qqline(resid(WHO.L),col="blue")
```

Residual standard error is 9.371 and F-statistic is 65.26. $R^2$ is just 0.2577. P-value is almost 0.

Residuals are not normally distributed so this model is not that good.

## 2.

Raise life expectancy to the 4.6 power (i.e., $LifeExp^{4.6}$).  Raise total expenditures to the 0.06 power (nearly a log transform, TotExp^.06). Plot $LifeExp^{4.6}$  as a function of $TotExp^{.06}$, and r re-run the simple regression model using the transformed variables.  Provide and interpret the F statistics, $R^2$, standard error, and p-values.   Which model is "better?"

```{r}
LifeExp <- WHO$LifeExp^4.6
TotExp <- WHO$TotExp^0.06

WHO.L.new <- lm(LifeExp ~ TotExp)

# Scatter Plot
plot(LifeExp~TotExp)
abline(WHO.L.new)

# Linear regression summary
summary(WHO.L.new)

# Residual Plot
plot(fitted(WHO.L.new), resid(WHO.L.new))
abline(h=0)

# Q-Q plot of residual
qqnorm(resid(WHO.L.new))
qqline(resid(WHO.L.new))
```

Residual standard error is 90490000 and F-statistic is 507.7. $R^2$ is 0.7298, which is better than in the first model. P-value is almost 0.

This is a pretty good model as the variability of residual plot is fairly constant having some outliers.


## 3.

Using the results from 2, forecast life expectancy when $TotExp^.06 =1.5$.  Then forecast life expectancy when $TotExp^.06=2.5$. 

```{r}
predict(WHO.L.new, data.frame(TotExp=c(1.5,2.5)) ,interval="predict")^(1/4.6)
```


## 4.

Build the following multiple regression model and interpret the F Statistics, $R^2$, standard error, and p-values.  How good is the model?

$LifeExp = \beta_0+\beta_1 \times PropMD + \beta_2 \times TotExp + \beta_3 \times PropMD \times TotExp$

```{r}
# Multiple linear regression
WHO.M <- lm(LifeExp ~ PropMD + TotExp + TotExp:PropMD, data=WHO)

# Multiple regression summary
summary(WHO.M)

# Residuals Plot
plot(fitted(WHO.M), resid(WHO.M))
abline(h=0)

# Q-Q plot of residual
qqnorm(resid(WHO.M))
qqline(resid(WHO.M))
```
Residual standard error is 8.765 and F-statistic is 34.49. P-value is almost 0.

Residuals are not normally distributed so this model is not that good similar to the first model.


## 5.

Forecast LifeExp when $PropMD=.03$ and $TotExp = 14$.  Does this forecast seem realistic?  Why or why not?

```{r}
predict(WHO.M, data.frame(PropMD=0.03, TotExp=14),interval="predict")
```

This forecast is not realistic. The prediction is 107.696 yrs with a 95% confidence interval [84.24791,131.1441].