---
title: "DATA605_HW10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem Statement

Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars.A guard agrees to make a series of bets with him. If Smith bets A dollars,he wins A dollars with probability .4 and loses A dollars with probability .6.

Find the probability that he wins 8 dollars before losing all of his money if

## a) he bets 1 dollar each time (timid strategy).

Using Gambler's Rule: 

$s=1\\$
$m=8\\$
$p=0.4\\$
$q=0.6\\$
$P=\frac{1-(\frac{q}{p})^s}{1-(\frac{q}{p})^m}\\$

```{r}
s=1
m=8
p=0.4
q=0.6
P=(1 - (0.6/0.4)^1) / (1 - (0.6/0.4)^8)
P
```

## b) he bets, each time, as much as possible but not more than necessary tobring his fortune up to 8 dollars (bold strategy).

In this case Smith will bet 1, wins 2, then bets 2, wins 4, then bets 4 and wins 8. That means in 3 successes he will get the bail amount.

so: $P_{bold}=0.4^3\\$

```{r}
P_bold=0.4**3
P_bold
```

## c) Which strategy gives Smith the better chance of getting out of jail?

b) gives Smith better chance of getting out of jail as the moves required as less than that of a). 